---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hLDA

<!-- badges: start -->
<!-- badges: end -->


The `hLDA` package is a wrapper around the `HLDA` class/functions of the 
`tomotopy` `python` library. It allows to fit hierarchical topic models
(hierarchical Latent Dirichlet Allocation) on matrix of count data where each
row is a sample (e.g. a document) and each column is a feature (e.g. a word). 
Element `(i,j)` of the count matrix provides the number of time a given 
feature `j` was found in document `i`.


## Installation

You can install the development version of hLDA like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to fit a hierarchical LDA model to
count data and to visualized the fitted parameters. This example fit hLDA to
random data, where no structure is expected.

```{r example}
library(hLDA)

set.seed(1)
M <- 10 # number of samples (e.g. documents)
N <- 20 # number of features (e.g. words)
x <- matrix(sample(0:100, N*M, replace = TRUE), M, N)
colnames(x) <- paste0(sample(letters, N, replace = TRUE), 1:N) # random feature names
m <- hLDA(x, depth = 3) # fitting the hLDA to the data

```

```{r plot, fig.height=10, fig.width=7}

plot_hLDA(m, title = "test with random data")

```


