---
title: "Introduction to hLDA"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to hLDA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hLDA)
```

The `hLDA` package is a wrapper around the `HLDA` class/functions of the 
`tomotopy` `python` library. It allows to fit hierarchical topic models
(hierarchical Latent Dirichlet Allocation) on matrix of count data where each
row is a sample (e.g. a document) and each column is a feature (e.g. a word). 
Element `(i,j)` of the count matrix provides the number of time a given 
feature `j` was found in document `i`.

The main functions are `hLDA` and a series of visualization functions that 
display the fitted parameters of the model.

The typical workflow is applied below on random data (where no structure is expected). 

```{r hLDA}

set.seed(1)
M <- 10 # number of samples (e.g. documents)
N <- 20 # number of features (e.g. words)
x <- matrix(sample(0:100, N*M, replace = TRUE), M, N)
colnames(x) <- paste0(sample(letters, N, replace = TRUE), 1:N) # random feature names
m <- hLDA(x, depth = 3) # fitting the hLDA to the data

```

```{r plot, fig.height=10, fig.width=7}

plot_hLDA(m, title = "test with random data")

```


